### 2016-05-19 2016-lrec-tyvmorph/poster.tex
more hargling
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@68627 72bbbca6-d526-0410-a7d9-f06f51895060

	}{ %Title (centered top)
		{%\vspace{0pt}\hspace{1cm} \
			{\titlefont \scshape{A finite-state morphological analyser for Tuvan}
			}
		}
	}{ %Authors (centered top, below title)
		%\vspace{-0.6em}
		\begin{center}
			\begin{minipage}[t]{7em}
				\begin{spacing}{0.4}
				{Francis M.\ Tyers}\\
				{\footnotesize UiT Norgga Árktalaš Universitehta \\\texttt{francis.tyers@uit.no}}
				\end{spacing}
			\end{minipage}
			\begin{minipage}[t]{12em}
				\begin{spacing}{0.4}
					{Jonathan North Washington}\\
					{\footnotesize Indiana University\\\texttt{jonwashi@indiana.edu}}
				\end{spacing}
			\end{minipage}
			\begin{minipage}[t]{8em} %{7.7em}
				\begin{spacing}{0.4}
					{Aziyana Bayyr-ool}\\
					{\footnotesize Сибирское отделение Российской академии наук\\\texttt{azikoa@mail.ru}}
				\end{spacing}
			\end{minipage}
			\begin{minipage}[t]{6em}
				\begin{spacing}{0.4}
					{Aelita Salchak}\\
					{\footnotesize Тываның Күрүне Университеди\\\texttt{aelita\_74@mail.ru}}
				\end{spacing}
			\end{minipage}
		\end{center}
	}{ %More eye catchers, on the right side
		\setlength\fboxsep{0.5em}
		\setlength\fboxrule{0pt}
		\fbox{\includegraphics[height=5.5em]{img/Tuvsu}}
		\includegraphics[height=5.4em]{img/soranif}
		%\hspace{2.5cm}
	}

@@

	\headerbox{What should we put here}{name=harglebargle,column=0,below=morphtrans}{
		\vspace{0.5in}

@@

		\headerbox{Development cycle}{name=development,below=harglebargle,span=1}{
		\centering
		\begin{tikzpicture}[xscale=1.45,yscale=2.6]%, auto]

@@

	\headerbox{Evaluation}{name=results,column=2,below=example}{ %lexicon}{
		%\begin{multicols}{2}	
		\begin{itemize}
			\item Naïve coverage calculated on 5-part corpus
		\end{itemize}
		\begin{center}
		\resizebox{0.9\textwidth}{!}{
		\begin{tabular}{lrr}
			\toprule
			 \textbf{Domain} & \textbf{Tokens} & \textbf{Coverage} (\%) \\
			\midrule
			 News       & 1,539,459 &  95.73  \\
			 Religion   & 746,124 &  93.84 \\
			 Literature & 297,830 &  91.96  \\
			 Encyclopaedic  & 276,547 & 90.86 \\
			 Folklore & 27,902 & 91.57  \\\cline{2-3}
			 Average    & -- & 92.79 \\
			\bottomrule
		\end{tabular}}
		\end{center}

		\begin{itemize}
			\item Good results reflect high accuracy
		\end{itemize}
		\begin{center}
		\resizebox{0.9\textwidth}{!}{
		\begin{tabular}{llrr}
			\toprule
				& \textbf{count} & \textbf{precision} & \textbf{recall} \\
			\midrule
			known tokens & 1024 & 0.99 & 0.97 \\
			all tokens & 1425 & 0.99 & 0.69 \\
			\bottomrule
		\end{tabular}}
		\end{center}
		%{\qipa ↑} quantitative eval\\
		%\newline
		%\vspace{0.01pt}\hfill{}qualitative eval {\qipa ↗}\\
		%\columnbreak
		\begin{itemize}
			\item Qualitative evaluation
		\end{itemize}

@@

		\headerbox{Morphotactics}{name=morphotactics,column=1,below=example}{
			\centering
			\includegraphics[width=0.9\textwidth]{img/dibuix}

>>>>

	}{ %Title (centered top)
		{%\vspace{0pt}\hspace{1cm} \
			{\titlefont \scshape{A finite-state morphological analyser for Tuvan}
			}
		}
	}{ %Authors (centered top, below title)
		%\vspace{-0.6em}
		\begin{center}
			\begin{minipage}[t]{8.5em} %{7em}
				\begin{spacing}{0.4}
				{Francis M.\ Tyers}\\
				{\footnotesize UiT Norgga Árktalaš Universitehta \\\texttt{francis.tyers@uit.no}}
				\end{spacing}
			\end{minipage}
			\begin{minipage}[t]{12em}
				\begin{spacing}{0.4}
					{Jonathan North Washington}\\
					{\footnotesize Indiana University\\\texttt{jonwashi@indiana.edu}}
				\end{spacing}
			\end{minipage}
			\begin{minipage}[t]{9em} %{7.7em}
				\begin{spacing}{0.4}
					{Aziyana Bayyr-ool}\\
					{\footnotesize Сибирское отделение Российской академии наук,~~\texttt{azikoa@mail.ru}}
				\end{spacing}
			\end{minipage}
			\begin{minipage}[t]{8em} %{6em}
				\begin{spacing}{0.4}
					{Aelita Salchak\vphantom{y}}\\
					{\footnotesize Тываның Күрүне Университеди\\\texttt{aelita\_74@mail.ru}}
				\end{spacing}
			\end{minipage}
		\end{center}
	}{ %More eye catchers, on the right side
		\setlength\fboxsep{0.5em}
		\setlength\fboxrule{0pt}
		\fbox{\includegraphics[height=5.5em]{img/Tuvsu}}
		\includegraphics[height=5.4em]{img/soranif}
		%\hspace{2.5cm}
	}

@@

	\headerbox{What should we put here}{name=harglebargle,column=0,below=morphtrans}{
		\vspace{0.35in}

@@

		\headerbox{Development cycle}{name=development,below=harglebargle,span=1}{
		\centering
		\begin{tikzpicture}[xscale=1.45,yscale=2.5]%, auto]

@@

	\headerbox{Evaluation}{name=results,column=2,below=example}{ %lexicon}{
		%\begin{multicols}{2}	
		\htwo{5-part corpus for naïve coverage}
		%\begin{itemize}
		%	\item Naïve coverage calculated on 5-part corpus
		%\end{itemize}
		\begin{center}
		\resizebox{0.9\textwidth}{!}{
		\begin{tabular}{lrr}
			\toprule
			 \textbf{Domain} & \textbf{Tokens} & \textbf{Coverage} (\%) \\
			\midrule
			 News       & 1,539,459 &  95.73  \\
			 Religion   & 746,124 &  93.84 \\
			 Literature & 297,830 &  91.96  \\
			 Encyclopaedic  & 276,547 & 90.86 \\
			 Folklore & 27,902 & 91.57  \\\cline{2-3}
			 Average    & -- & 92.79 \\
			\bottomrule
		\end{tabular}}
		\end{center}

		\htwo{Naïve coverage results}
		%\begin{itemize}
		%	\item Good results reflect high accuracy
		%\end{itemize}
		\begin{center}
		\resizebox{0.9\textwidth}{!}{
		\begin{tabular}{llrr}
			\toprule
				& \textbf{count} & \textbf{precision} & \textbf{recall} \\
			\midrule
			known tokens & 1024 & 0.99 & 0.97 \\
			all tokens & 1425 & 0.99 & 0.69 \\
			\bottomrule
		\end{tabular}}
		\end{center}
		%{\qipa ↑} quantitative eval\\
		%\newline
		%\vspace{0.01pt}\hfill{}qualitative eval {\qipa ↗}\\
		%\columnbreak

		\htwo{Qualitative evaluation}
		%\begin{itemize}
		%	\item Qualitative evaluation
		%\end{itemize}

@@

		\headerbox{Morphotactics}{name=morphotactics,column=1,below=example}{
			\begin{itemize}
				\item Introduction of quasi-derivational verbal morphotactics
			\end{itemize}
			\centering
			\includegraphics[width=0.9\textwidth]{img/dibuix}
